The Lasting Shadows of Economic Downturns

### 2024-02-14 outputs/paper/paper.qmd
Update paper.qmd

# Introduction
*This reproduction was performed after a replication on the Social Science Reproduction platform: ****[link here](https://www.socialsciencereproduction.org/reproductions/f4c25f83-2c8b-448e-be76-760e02694112/index)***

@@

## Measurement

>>>>

# Introduction
*This reproduction was performed after a replication on the Social Science Reproduction platform: ****[link here](update the link!!!)***

@@

## Methodology and Measurement
